%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience (7+y)}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {FinTech core team} % Position description
    {Yandex} % Organization
    {Largest big tech in CIS} % Company description
    {3y 5m{\enskip\cdotp\enskip}Full-time} % Location
    {Oct. 2023 - Mar. 2025{\enskip\cdotp\enskip}Belgrade, Serbia} % Date(s)
    {
      \cvdesctitle{Key achievements}
      \begin{cvitemstitled} % Description(s) of tasks/responsibilities
        \item {Redesigned core of the payment engine to improve load capacity by 50\%, simplify and reduce cost for launching new services.}
        \item {Reduced hardware costs by 20\% and improved core service response times by 40\% (600ms \rightarrow 350ms) through backend optimization.}
        \item {Reduced the average time-to-market from $\sim$1 week to $\sim$1 day by improving CI/CD process for the payment engine.}
      \end{cvitemstitled}
      \cvdesctitle{Ownership/responsibilities}
      \begin{cvitemstitledended}
        \item {Supporting the team lead in aligning quarterly OKRs with business goals, taking part in planning, prioritization, and decomposition to ensure clear focus and efficient execution.}
        \item {Developing features and improving fault tolerance (achieving 99.999\% uptime) for the high-load payment system handling \$50M+ annual transactions.}
        \item {Handled on-call production duty for the high-load system (10,000+ RPS, 1M+ daily transactions).}
        \item {Conducted 20+ technical interviews to support the company hiring process.}
      \end{cvitemstitledended}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {FinTech core team} % Position description
    {} % Organization
    {} % Company description
    {} % Location
    {Nov. 2021 - Oct. 2023{\enskip\cdotp\enskip}Moscow, Russia} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced incident response time by 80\% by implementing an observability stack: metrics, dashboards, and alerts for different parts of the payment engine.}
        \item {Mitigated infrastructure risks by contributing to a purpose-built ORM and migrating a 1TB data collection to a cloud DB with zero downtime.}
        \item {Improved service reliability by launching testing duty rotation and training developers in structured incident response.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Cybersecurity products marketplace} % Position description
    {BI.ZONE} % Organization
    {B2B cybersecurity products} % Company description
    {1y 8m{\enskip\cdotp\enskip}Full-time} % Location
    {Mar. 2020 - Oct. 2021{\enskip\cdotp\enskip}Moscow, Russia} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built backend from scratch for 2 cybersecurity services (API + administration + async tasks) in a cross-functional team.}
        \item {Owned backend development for several production services — added features and optimizations, handled bug fixes.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {} % Position description
    {Media Machines Laboratory} % Organization
    {B2B digital marketing automation} % Company description
    {7m{\enskip\cdotp\enskip}Full-time} % Location
    {Sep. 2019 - Mar. 2020{\enskip\cdotp\enskip}Moscow, Russia} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated Google Ads and Facebook Graph APIs — enabled in-platform ad forecasting for media plan generation.}
        \item {Built Google Data Studio connector — retained 2 key clients and enabled a new direction for attracting clients.}
        \item {Improved media plan generation algorithm — reduced processing time by 20\%.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {} % Position description
    {START.ru} % Organization
    {B2C streaming service} % Company description
    {7m{\enskip\cdotp\enskip}Full-time} % Location
    {Feb. 2019 - Aug. 2019{\enskip\cdotp\enskip}Moscow, Russia} % Date(s)
    {}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {} % Position description
    {DC-systems.ru} % Organization
    {B2B speech analyzing} % Company description
    {1y 7m{\enskip\cdotp\enskip}Full-time} % Location
    {Aug. 2017 - Feb. 2019{\enskip\cdotp\enskip}Moscow, Russia} % Date(s)
    {}

%---------------------------------------------------------
\end{cventries}
